Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-12 tests-vandv.tex
added matt's changes.

After the test problems are selected by the test runner script, they
are run in succession using either the \enzo\ executable contained
within that distribution or an external executable built from another \enzo\
version and specified by the user.  This allows for any version of the
code to be tested with an identical set of test problems.  After
running the test problem simulations, the test runner then performs a
series of basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics, such as extrema, mean and variance, on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results that are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  In
Section~\ref{sec.tests.problems}, we describe some of the key test
problems that are used to verify proper behavior.  All of these test
problems, as well as the scripts to generate the figures from them,
are available in the \enzo\ test suite, allowing the interested reader
to regenerate all of the figures in Section~\ref{sec.tests.compare}
using the \textit{`methodpaper'} suite of test problems.

>>>>

After the test problems are selected by the test runner script, they
are run in succession using either the \enzo\ executable contained
within that distribution or an external executable built from another \enzo\
version and specified by the user.  This allows for any version of the
code to be tested with an identical set of test problems.  After
running the test problem simulations, the test runner then performs a
series of basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics, such as extrema, mean and variance, on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results that are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  In
Section~\ref{sec.tests.problems}, we describe some of the key test
problems that are used to verify proper behavior.  All of these test
problems, as well as the scripts to generate the figures from them,
are available at \url{http://bitbucket.org/bwoshea/enzo-method-paper},
the BitBucket repository for the \enzo\ method paper.  The
\texttt{test\_problems} subdirectory in this repository contains all of
the files necessary to regenerate all of the figures in
Section~\ref{sec.tests.compare}.  We note for completeness that all of
the figures were generated using \texttt{yt} version 2.5.3 and the
\url{https://bitbucket.org/enzo/enzo-dev} repository of \enzo\ with
changeset \texttt{5d8c412}.
